---
title: "Project presentation"
author: "Neil Rankin"
date: "18/07/2019"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

## Types of insights

- Are there differences in outcomes between males and females?
   + Does this justify different types of interventions?
 
- What types of labour market pathways are there in the data?
   + Are there certain types of characteristics associated with these different pathways?
 
- Are there particular groups who are particularly disadvantaged?

## Types of insights

- What matters most for a 'successful' outcome?
    + Are these changable and what could be done to change them?
    
- Does age matter?
    + Should interventions differ depending on how old someone is?
    
- Is there seasonality in hiring?
    + Do certain types of profiles benefit from this?
    
## Types of insights

- Is there a particular length or number of jobs a person requires to be "secure"?

- How does the sample change?
    + With time?
    + Across survey numbers?
    + Between men and women?
    + Between provinces?
    
- Is there a provincial or location aspect?
    + Could certain types of people benefit from moving to different areas?
    
## Project setup

- Repo: `..._pink?`

- Must run on another machine (machine independent)

- Model will be tested on script using test data in similar format to train data
    + Need a file that cleans (`clean_data.R`) and produces an `RDS` file
    + Then need a model file which creates the model on your training data and then which can be used to predict (`model.R`)
    + In a sub-folder called `submission`